Outstanding Title

### 2017-04-19 writing/EpiDraft.Rmd
Scrape scrape

>>>>

#MidAtlantic 2006:
i <- 1:9
url1to9 <- i %>% map(~paste("https://wonder.cdc.gov/mmwr/mmwr_1995_2014.asp?mmwr_year=2006&mmwr_week=0", as.character(.x), "&mmwr_table=2C&request=Submit&mmwr_location=", sep=""))
i <- 10:53
url10to53 <- i %>% map(~paste("https://wonder.cdc.gov/mmwr/mmwr_1995_2014.asp?mmwr_year=2006&mmwr_week=", as.character(.x), "&mmwr_table=2C&request=Submit&mmwr_location=", sep=""))
url2006 <- c(url1to9, url10to53)
ma2006 <- url2006 %>% map(~read_html(.x)) %>% map(~html_nodes(.x, 'tr:nth-child(13) td:nth-child(12)')) %>% map(~html_text(.x))
as.numeric(ma2006)
